### 2019-04-02 papers/journal/conclusion.tex
Uniform use of the title without :

In this paper, we presented encodings of the synthesis problems
that may arise from VTSs.
%
We demonstrated that our tool based on the encodings
scale up to the relevant sizes of the VTSs for some synthesis queries.
%
Our tool timed out on larger examples.
%
We are working to improve the performance of our tool.
%
We will take this tool to the biologists and develop wet experiments that may validate some synthesis results from the tool.
%
Our model of VTSs is static graphs.
%
In future, we will study the dynamic behaviors of VTSs.
%
It will allow us to predict behaviors after the perturbations in the VTSs
and more ways to test the predicted synthesis results.\\

@@

\textbf{Encode Dynamic behaviour of the VTS:} A major aspect of the biological cell’s VTS that the current model is missing is compartment maturation. Compartments of the cell are not in steady state; rather they are changing in molecular composition due to imbalances in incoming and outgoing molecular flux on vesicles.
Maturation  is  evident  in  the  Golgi  apparatus  and  in  the  endocytic system. 
Including this behaviour of the compartments in the model would allow it to make more accurate predictions.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

\noindent In this paper, we presented encodings of the synthesis problems
that may arise from VTSs.
%
We demonstrated that our tool based on the encodings
scale up to the relevant sizes of the VTSs for some synthesis queries.
%
Our tool timed out on larger examples.
%
We are working to improve the performance of our tool.
%
We will take this tool to the biologists and develop wet experiments that may validate some synthesis results from the tool.
%
Our model of VTSs is static graphs.
%
In future, we will study the dynamic behaviors of VTSs.
%
It will allow us to predict behaviors after the perturbations in the VTSs
and more ways to test the predicted synthesis results.\\

@@

\textbf{Encode Dynamic behaviour of the VTS} A major aspect of the biological cell’s VTS that the current model is missing is compartment maturation. Compartments of the cell are not in steady state; rather they are changing in molecular composition due to imbalances in incoming and outgoing molecular flux on vesicles.
Maturation  is  evident  in  the  Golgi  apparatus  and  in  the  endocytic system. 
Including this behaviour of the compartments in the model would allow it to make more accurate predictions.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2019-04-02 papers/journal/encoding.tex
added pairing matrix constraint in qbf
Uniform use of the title without :

%\externaldocument{sat-table}
%\externaldocument{smt-table}
%\externaldocument{qbf-table}

In the previous section, we have discussed four problems.
%
In this section we will present encodings fof the
$\fsmt$ search, $\fbmc$ search, $\fqbf$ search and synthesis problems.
%
We will start with the $\fsmt$ search encoding and later present the
contrast with the $\fbmc$ encoding.

@@

%\subsection{Boolean satisfiability of the search problem}
We translate the search problem into a Boolean satisfiability
problem and use SMT solvers to find the satisfying VTSs.
%
We will first present the variables used to encode the
VTSs and the properties.
%
Afterwards, we will present the constraints corresponding to the
properties.

@@

Our first attempt was to encode the existential condition check as a $\fbmc$ search problem~\cite{shukla2017discovering}.
%
%In this section we will present the $\fbmc$ encoding of the same.
%
Although the techniques used for $\fbmc$ and $\fsmt$ is very different because we are not unrolling the complete program in the case of $\fbmc$, the encoding is not considerably different.
% 
The $\fbmc$ search encoding differs with the presented $\fsmt$ encoding in the way variables are represented and how we encode reachability (both for the stability and connectivity).  
%
Here, we will only present the stability encoding.
%the rest of the encodings are similar to the one presented in the previous section, Section~\ref{enc:smt}.

@@

\subsubsection{The key difference in the reachability encoding}:
The key improvement of the $\fsmt$ search encoding over the $\fbmc$ is the
encoding of reachability.
% which was done using an enumeration of paths.
%
In the $\fbmc$ encoding, reachability is encoded by enumerating all the possible paths using non-determinism.
%
This encoding is non-optimal in the sense that in the worst case an exponential number of paths needs to be explored.
%
Whereas in the $\fsmt$ encoding, reachability is encoded in two different
ways in constraints $\texttt{Paths}(r)$ and $\texttt{FReach}(d,r')$.
%
The reachability is recursively defined in~$\texttt{FReach}(d,r')$ and has
trivial solutions by making all $r'$s true.
%
However, the trivial solutions are disallowed by constraint~$\texttt{Connected}(r')$ and we find
only the solutions that captures the evidence of non-reachability.
%
On the other hand, we have added length of paths in our reachability encoding in constraint~$\texttt{Paths}(r)$, which needs relatively more auxiliary variables.
%
This is because constraint~$\texttt{Loop}(r)$ has only positive
occurrences of the reachability variables and if we had defined
$r$s in~$\texttt{Paths}(r)$ without paths,
the circular dependencies in the recursive definitions of $r$s
may have resulted in spurious satisfying assignments that
do not encode reachability.
%
By adding the path length, we break the circular dependencies, the
constraint remains polynomial in size, and satisfying assignments only
correspond to correct reachability.

@@

%if all the pairs of the present molecule are present on the same edge than all of them inhibit each other resulting in making all the molecules inactive, we term this process ``pairing inhibition".
%
The constraints for the variants can be given to a SAT or a SMT solver to find
VTSs that belong to the variants.
\subsection{Encoding for $\fqbf$ search problem}\label{enc:univ-cond}
%
\input{satqbf-table}
Recall that the specification for universal condition~\ref{sec:property} requires quantifier alternation. 
%
Most SAT solvers can not efficiently handle the quantifier in the formulas. 
% 
Although, it is possible to encode the universal condition as a SAT or SMT problem.
%
There is always a danger of a blow-up in the formula size, making it harder for the SAT solver to handle. 
%Which may blow up the formula size for the solver to solve.
% 
As an experiment, we have implemented a direct SMT version (encoding not presented) of the universal problem extending the current $\fsmt$ search encodings.
%
The basic idea is to conjunct the formula for each combination value of the quantified variable. 
%
The table~\ref{tab:satqbf-graph}, shows the search results of this encoding for the universal condition with 4 nodes and 3-connected graphs. 
%
The connectivity constraint and connectedness constraints are tagged with subscript $U$, $\texttt{StabilityC}_{U}$, $\texttt{Connected}(k)_{U}$,  to distinguish from earlier presented encodings of existential condition.
%
The SMT extended version was not able to scale it to the desired results and either timed-out (T/O) or ran out of memory (M/O).
%
This can be due to the fact that directly translating a quantified formula into a quantifier-free  by introducing a vector of variables for each boolean possibility will blow up the size of the formula and may not be solvable by a solver.
%
%
\subsubsection{$\fqbf$ search encoding of the universal condition:}
We will describe several constraints that encode universal condition based on QBF formulation in this section.
%
To avoid cumbersome notation, we will not explicitly write the ranges
of the indexing in the constraints.
%
$i$ and $j$ will range over nodes, i.e., from $1$ to $\nu$.
%
$m$ will range over molecules, i.e., from $1$ to $\mu$.
%
$q$ will range over edges between two nodes, i.e., from $1$ to $\pi$.
%

We will rewrite \texttt{PairingC} constraint using quantifiers.
%
The \texttt{QPairingC} states that all molecules are divided into two types
using $qr_m$ bit, which encodes if $m$ belongs to one type or another,
and any fusing set of molecules must have three molecules involved
%
We encode this constraint as a QBF.
\begin{align*}
 \texttt{QPairingC} =\;&
\exists qr. \Land\limits_{\mathrlap{m_1,m_2,m_3,m_4}\;\;}
(p_{\{m_1,m_2,m_3,m_4\}} \limplies qr_{m_1} + qr_{m_2} + qr_{m_3} + qr_{m_4} = 3)
\end{align*}
Using constraints for VTS from Section~\ref{enc:smt}, we encode the basic consistency of VTSs. 
%
%Recall that the molecule set is divided into 3:1 Q and R pairs (or partition).
\begin{align*}
%\texttt{EdgeC} =\;&\hspace{-1ex}\bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
%\land
%\bigwedge\limits_{i,q} \neg e_{i,i,q}
%\land
%% \tag{\texttt{NodeC}}\label{eq:f0}\\
%\bigwedge\limits_{\mathclap{i,j,q,m}} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
%\\
%\texttt{ActivityC} =\;&
%\bigwedge\limits_{\mathclap{i,j,q,m}} b_{i,j,q,m} \limplies e_{i,j,q,m} \quad\land\quad
%\bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
%% \tag{V2}\label{eq:f1}\\
%\\
%\texttt{PairingC} =\;&
%\exists qr. \Land\limits_{\mathrlap{m_1,m_2,m_3,m_4}\;\;}
%(p_{\{m_1,m_2,m_3,m_4\}} \limplies qr_{m_1} + qr_{m_2} + qr_{m_3} + qr_{m_4} = 3) 
%% \land\\ 
%%   & \quad\quad\quad ( m_1 = m_2 = m_3 = m_4  \limplies \lnot p_{m_1,m_2,m_3,m_4} )
%% \bigwedge\limits_{m} 
%% (\Lor\limits_{m'} p_{mm'} \limplies \Land_{m'} \lnot p_{m'm} ) \land
%% (\Lor\limits_{m'} p_{m'm} \limplies \Land_{m'} \lnot p_{mm'} )
%\\
%\texttt{Fusion1} =\;&
%\bigwedge\limits_{i,j,q} e_{i,j,q} \limplies
%\bigvee_{{m_1,m_2,m_3,m_4}} (\Land_{l=1}^4 ( b_{i,j,q,m_l} \lor a_{j,m_l} ) \land 
%\Lor\limits_{l=1}^4 b_{i,j,q,m_l} \land\\
%& \qquad \qquad \qquad \qquad \Lor\limits_{l=1}^4 a_{j,m_l}\land p_{\{m_1,m_2,m_3,m_4\}})
%\\
%\texttt{Fusion2} =\;&
%\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies \\
%& \hspace{2cm} \neg 
%\bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land .. \land a_{j^{\prime},m_4^{\prime}} \land p_{\{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4\}})
\texttt{Consistancy} =\;& \texttt{EdgeC} \land
\texttt{ActivityC} \land \texttt{QPairingC} \land
\texttt{Fusion} 
\end{align*}
%\texttt{EdgeC} states that each edge has at least one molecule,
%there are no self loops, and edge labels are consistent with node labels.   
%\texttt{ActivityC} states that active molecule are present.
%\texttt{PairingC} states that all molecules are divided into two types
%using $qr_m$ bit, which encodes if $m$ belongs to one type or another,
%and any fusing set of molecules must have three molecules involved
%from one type and one molecule from the other.
%\texttt{Fusion1}, and \texttt{Fusion2} states the well-fused condition.
%\texttt{Consistancy} is the conjunction of all of the above.

@@

\subsection{Encoding for the synthesis problem}
In this section, we will present our synthesis method for
the synthesis problems.
%
%We assume that certain properties of the partial input VTS always hold, for example, the activity of the molecules and well-fused constraints. 
%
%Whereas properties like stability and connectivity discussed in the previous sections may not.
%
Here, we use these two properties stability and connectivity against which we perform our synthesis. 
%
The encoding can be easily extended to accommodate other interesting properties.

@@

In the later synthesis problems, we will construct a similar QBF
formula with same first two parts and the last two are due the
requirements of the synthesis problem.

\paragraph{\bf Fixing VTS by adding molecules to the labels:}
The system may also be fixed only by modifying labels on the edges or the nodes instead
of adding edges.
%
Here let us consider only adding molecules to the labels of edges.
%
In the following, the formula encodes that only $slimit$ edge labels may be added.
\begin{align*}
&\texttt{AddLabelEdge}(slimit) = 
\sum~\texttt{UnknwonEdgeLabel}  \leq slimit\\
& \texttt{FixedForLabel} = \texttt{PresentCons} \land \texttt{UnknownActive} \land\\
& \quad \quad \lnot \Lor \texttt{AbsentE} \;\union\;
\texttt{AbsentNLabel} \;\union\;
\texttt{AbsentP}\\
&\texttt{SynthLabel}(slimit) = \\
& \quad\quad
(  \texttt{Consistancy}\land \texttt{Property} \land
\texttt{FixedForLabel} \land \texttt{AddLabelEdge}(slimit) )
\end{align*} 
Similar to the previous encoding, we solve the
satisfiability of the above formula to obtain additional molecules
that may be added to the edge labels to satisfy the properties.

\subsubsection{Fixing VTS by learning activity functions:}
Now we consider a scenario where some of the activity functions for
some of the molecules are missing.
%
The activity functions are $\mu$-input Boolean functions.
%
First, we choose a class of formulas for the candidate functions.
%
We encode the candidates in a formula with parameters.
%
By assigning different values for the parameters, a solver may select
different candidates for the activity functions.
%
We will illustrate only one class of formulas.
%
However, we support other classes of formulas, for example, $k$-CNF.

@@

\subsubsection{Fixing VTS by both adding/deleting parts:}
%
Now we will consider repairing of VTS by allowing not only addition but also
deletion of the molecules, edges, functions, or pairing matrix.
%
We have encoded the repairing in our tool by introducing flip bits
for each variable that is modifiable in the VTS.
%
We illustrate the repairing on one class of variables and rest can be
easily extended.
%
Let us consider repairing of node labels.
%
For each bit $n_{i,m}$, we create a bit $flip_{i,m}$.
%
We add constraints that take xor of VTS assigned values for  $n_{i,m}$
and $flip_{i,m}$.
%
We also limit the number of $flip_{i,m}$ that can be true, therefore
limiting the number of flips.
%
The above constraints are encoded in $\texttt{FlipN}(slimit)$.
\begin{align*}
&\texttt{FlipN}(slimit,flip) = \Land \{n_{i,m}\lxor flip_{i,m}| m \in \nlabel(i) \land i \in \nodes \} \land \\
& \quad \quad \quad
\Land \{ \lnot n_{i,m}\lxor flip_{i,m}| m \not \in \nlabel(i) \land i \in \nodes \} \land  \sum\limits_{i,m} flip_{i,m} \leq slimit
\end{align*}
%
Similar to the earlier variations, we construct
$\texttt{SynthRepairNode}(slimit)$ for the repair.
%
In that, $\texttt{FixedForNodeRepair}$ encodes all the parts of VTS that do not change.
\begin{align*}
% \\ 
& \texttt{FixedForNodeRepair} =  \texttt{PresentE} \land  
\texttt{PresentP} \land \texttt{KnownActiveE} 
\land \\
& \quad \texttt{UnknownActive} \land \texttt{KnownActiveN} \land \lnot 
\Lor \texttt{AbsentE} \;\union\; \texttt{AbsentNLabel} \;\union\;
\texttt{AbsentP}\\
&\texttt{SynthRepairNode}(slimit,flip) = \\
& \quad\quad
(  \texttt{Consistancy}\land \texttt{Property} \land
\texttt{FixedForNodeRepair} \land \texttt{FlipN}(slimit,flip) )
\end{align*}
A satisfying model of $\texttt{SynthRepairNode}(slimit,flip)$ will assign some
$flip$ bits to true.
We will learn from the assignments the needed modifications in the VTS.

>>>>

%\externaldocument{sat-table}
%\externaldocument{smt-table}
%\externaldocument{qbf-table}
\noindent In the previous section, we have discussed four problems.
%
In this section we will present encodings fof the
$\fsmt$ search, $\fbmc$ search, $\fqbf$ search and synthesis problems.
%
We will start with the $\fsmt$ search encoding and later present the
contrast with the $\fbmc$ encoding.

@@

%\subsection{Boolean satisfiability of the search problem}
\noindent We translate the search problem into a Boolean satisfiability
problem and use SMT solvers to find the satisfying VTSs.
%
We will first present the variables used to encode the
VTSs and the properties.
%
Afterwards, we will present the constraints corresponding to the
properties.

@@

\noindent Our first attempt was to encode the existential condition check as a $\fbmc$ search problem~\cite{shukla2017discovering}.
%
%In this section we will present the $\fbmc$ encoding of the same.
%
Although the techniques used for $\fbmc$ and $\fsmt$ is very different because we are not unrolling the complete program in the case of $\fbmc$, the encoding is not considerably different.
% 
The $\fbmc$ search encoding differs with the presented $\fsmt$ encoding in the way variables are represented and how we encode reachability (both for the stability and connectivity).  
%
Here, we will only present the stability encoding.
%the rest of the encodings are similar to the one presented in the previous section, Section~\ref{enc:smt}.

@@

\subsubsection{The key difference in the reachability encoding}
The key improvement of the $\fsmt$ search encoding over the $\fbmc$ is the
encoding of reachability.
% which was done using an enumeration of paths.
%
In the $\fbmc$ encoding, reachability is encoded by enumerating all the possible paths using non-determinism.
%
This encoding is non-optimal in the sense that in the worst case an exponential number of paths needs to be explored.
%
Whereas in the $\fsmt$ encoding, reachability is encoded in two different
ways in constraints $\texttt{Paths}(r)$ and $\texttt{FReach}(d,r')$.
%
The reachability is recursively defined in~$\texttt{FReach}(d,r')$ and has
trivial solutions by making all $r'$s true.
%
However, the trivial solutions are disallowed by constraint~$\texttt{Connected}(r')$ and we find
only the solutions that captures the evidence of non-reachability.
%
On the other hand, we have added length of paths in our reachability encoding in constraint~$\texttt{Paths}(r)$, which needs relatively more auxiliary variables.
%
This is because constraint~$\texttt{Loop}(r)$ has only positive
occurrences of the reachability variables and if we had defined
$r$s in~$\texttt{Paths}(r)$ without paths,
the circular dependencies in the recursive definitions of $r$s
may have resulted in spurious satisfying assignments that
do not encode reachability.
%
By adding the path length, we break the circular dependencies, the
constraint remains polynomial in size, and satisfying assignments only
correspond to correct reachability.

@@

%if all the pairs of the present molecule are present on the same edge than all of them inhibit each other resulting in making all the molecules inactive, we term this process ``pairing inhibition".
%
The constraints for the variants can be given to a SAT or a SMT solver to find
VTSs that belong to the variants.
\subsection{Encoding for $\fqbf$ search problem}\label{enc:univ-cond}
%
\input{satqbf-table}
\noindent The specification for universal condition~\ref{sec:property} requires quantifier alternation. 
%
Most SAT solvers can not efficiently handle the quantifier in the formulas. 
% 
Although, it is possible to encode the universal condition as a SAT or SMT problem.
%
There is always a danger of a blow-up in the formula size, making it harder for the SAT solver to handle. 
%Which may blow up the formula size for the solver to solve.
% 
As an experiment, we have implemented a direct SMT version (encoding not presented) of the universal problem extending the current $\fsmt$ search encodings.
%
The basic idea is to conjunct the formula for each combination value of the quantified variable. 
%
The table~\ref{tab:satqbf-graph}, shows the search results of this encoding for the universal condition with 4 nodes and 3-connected graphs. 
%
The connectivity constraint and connectedness constraints are tagged with subscript $U$, $\texttt{StabilityC}_{U}$, $\texttt{Connected}(k)_{U}$,  to distinguish from earlier presented encodings of existential condition.
%
The SMT extended version was not able to scale it to the desired results and either timed-out (T/O) or ran out of memory (M/O).
%
This can be due to the fact that directly translating a quantified formula into a quantifier-free  by introducing a vector of variables for each boolean possibility will blow up the size of the formula and may not be solvable by a solver.
%
%
\subsubsection{$\fqbf$ search encoding of the universal condition}
We will describe several constraints that encode universal condition based on QBF formulation in this section.
%
To avoid cumbersome notation, we will not explicitly write the ranges
of the indexing in the constraints.
%
$i$ and $j$ will range over nodes, i.e., from $1$ to $\nu$.
%
$m$ will range over molecules, i.e., from $1$ to $\mu$.
%
$q$ will range over edges between two nodes, i.e., from $1$ to $\pi$.
%

We rewrite \texttt{PairingC} constraint using quantifiers.
%
The \texttt{QPairingC} states that all molecules are divided into two types
using $qr_m$ bit, which encodes if $m$ belongs to one type or another,
and any fusing set of molecules must have three molecules involved
%
We encode this constraint as a QBF.
\begin{align*}
 \texttt{QPairingC} =\;&
\exists qr. \Land\limits_{\mathrlap{m_1,m_2,m_3,m_4}\;\;}
(p_{\{m_1,m_2,m_3,m_4\}} \limplies qr_{m_1} + qr_{m_2} + qr_{m_3} + qr_{m_4} = 3)
\end{align*}
Using constraints for VTS from Section~\ref{enc:smt}, we encode the basic consistency of VTSs. 
%
%Recall that the molecule set is divided into 3:1 Q and R pairs (or partition).
\begin{align*}
%\texttt{EdgeC} =\;&\hspace{-1ex}\bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
%\land
%\bigwedge\limits_{i,q} \neg e_{i,i,q}
%\land
%% \tag{\texttt{NodeC}}\label{eq:f0}\\
%\bigwedge\limits_{\mathclap{i,j,q,m}} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
%\\
%\texttt{ActivityC} =\;&
%\bigwedge\limits_{\mathclap{i,j,q,m}} b_{i,j,q,m} \limplies e_{i,j,q,m} \quad\land\quad
%\bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
%% \tag{V2}\label{eq:f1}\\
%\\
%\texttt{PairingC} =\;&
%\exists qr. \Land\limits_{\mathrlap{m_1,m_2,m_3,m_4}\;\;}
%(p_{\{m_1,m_2,m_3,m_4\}} \limplies qr_{m_1} + qr_{m_2} + qr_{m_3} + qr_{m_4} = 3) 
%% \land\\ 
%%   & \quad\quad\quad ( m_1 = m_2 = m_3 = m_4  \limplies \lnot p_{m_1,m_2,m_3,m_4} )
%% \bigwedge\limits_{m} 
%% (\Lor\limits_{m'} p_{mm'} \limplies \Land_{m'} \lnot p_{m'm} ) \land
%% (\Lor\limits_{m'} p_{m'm} \limplies \Land_{m'} \lnot p_{mm'} )
%\\
%\texttt{Fusion1} =\;&
%\bigwedge\limits_{i,j,q} e_{i,j,q} \limplies
%\bigvee_{{m_1,m_2,m_3,m_4}} (\Land_{l=1}^4 ( b_{i,j,q,m_l} \lor a_{j,m_l} ) \land 
%\Lor\limits_{l=1}^4 b_{i,j,q,m_l} \land\\
%& \qquad \qquad \qquad \qquad \Lor\limits_{l=1}^4 a_{j,m_l}\land p_{\{m_1,m_2,m_3,m_4\}})
%\\
%\texttt{Fusion2} =\;&
%\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies \\
%& \hspace{2cm} \neg 
%\bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land .. \land a_{j^{\prime},m_4^{\prime}} \land p_{\{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4\}})
\texttt{Consistancy} =\;& \texttt{EdgeC} \land
\texttt{ActivityC} \land \texttt{QPairingC} \land
\texttt{Fusion} 
\end{align*}
%\texttt{EdgeC} states that each edge has at least one molecule,
%there are no self loops, and edge labels are consistent with node labels.   
%\texttt{ActivityC} states that active molecule are present.
%\texttt{PairingC} states that all molecules are divided into two types
%using $qr_m$ bit, which encodes if $m$ belongs to one type or another,
%and any fusing set of molecules must have three molecules involved
%from one type and one molecule from the other.
%\texttt{Fusion1}, and \texttt{Fusion2} states the well-fused condition.
%\texttt{Consistancy} is the conjunction of all of the above.

@@

\subsection{Encoding for the synthesis problem}
\noindent In this section, we will present our synthesis method for
the synthesis problems.
%
%We assume that certain properties of the partial input VTS always hold, for example, the activity of the molecules and well-fused constraints. 
%
%Whereas properties like stability and connectivity discussed in the previous sections may not.
%
Here, we use these two properties stability and connectivity against which we perform our synthesis. 
%
The encoding can be easily extended to accommodate other interesting properties.

@@

In the later synthesis problems, we will construct a similar QBF
formula with same first two parts and the last two are due the
requirements of the synthesis problem.
%
\subsubsection{Fixing VTS by adding molecules to the labels}
The system may also be fixed only by modifying labels on the edges or the nodes instead
of adding edges.
%
Here let us consider only adding molecules to the labels of edges.
%
In the following, the formula encodes that only $slimit$ edge labels may be added.
\begin{align*}
&\texttt{AddLabelEdge}(slimit) = 
\sum~\texttt{UnknwonEdgeLabel}  \leq slimit\\
& \texttt{FixedForLabel} = \texttt{PresentCons} \land \texttt{UnknownActive} \land\\
& \quad \quad \lnot \Lor \texttt{AbsentE} \;\union\;
\texttt{AbsentNLabel} \;\union\;
\texttt{AbsentP}\\
&\texttt{SynthLabel}(slimit) = \\
& \quad\quad
(  \texttt{Consistancy}\land \texttt{Property} \land
\texttt{FixedForLabel} \land \texttt{AddLabelEdge}(slimit) )
\end{align*} 
Similar to the previous encoding, we solve the
satisfiability of the above formula to obtain additional molecules
that may be added to the edge labels to satisfy the properties.

\subsubsection{Fixing VTS by learning activity functions}
Now we consider a scenario where some of the activity functions for
some of the molecules are missing.
%
The activity functions are $\mu$-input Boolean functions.
%
First, we choose a class of formulas for the candidate functions.
%
We encode the candidates in a formula with parameters.
%
By assigning different values for the parameters, a solver may select
different candidates for the activity functions.
%
We will illustrate only one class of formulas.
%
However, we support other classes of formulas, for example, $k$-CNF.

@@

\subsubsection{Fixing VTS by both adding/deleting parts}
%
Now we will consider repairing of VTS by allowing not only addition but also
deletion of the molecules, edges, functions, or pairing matrix.
%
We have encoded the repairing in our tool by introducing flip bits
for each variable that is modifiable in the VTS.
%
We illustrate the repairing on one class of variables and rest can be
easily extended.
%
Let us consider repairing of node labels.
%
For each bit $n_{i,m}$, we create a bit $flip_{i,m}$.
%
We add constraints that take xor of VTS assigned values for  $n_{i,m}$
and $flip_{i,m}$.
%
We also limit the number of $flip_{i,m}$ that can be true, therefore
limiting the number of flips.
%
The above constraints are encoded in $\texttt{FlipN}(slimit)$.
\begin{align*}
&\texttt{FlipN}(slimit,flip) = \Land \{n_{i,m}\lxor flip_{i,m}| m \in \nlabel(i) \land i \in \nodes \} \land \\
& \quad \quad \quad
\Land \{ \lnot n_{i,m}\lxor flip_{i,m}| m \not \in \nlabel(i) \land i \in \nodes \} \land  \sum\limits_{i,m} flip_{i,m} \leq slimit
\end{align*}
%
Similar to the earlier variations, we construct
$\texttt{SynthRepairNode}(slimit)$ for the repair.
%
In that, $\texttt{FixedForNodeRepair}$ encodes all the parts of VTS that do not change.
\begin{align*}
% \\ 
& \texttt{FixedForNodeRepair} =  \texttt{PresentE} \land  
\texttt{PresentP} \land \texttt{KnownActiveE} 
\land \\
& \quad \texttt{UnknownActive} \land \texttt{KnownActiveN} \land \lnot 
\Lor \texttt{AbsentE} \;\union\; \texttt{AbsentNLabel} \;\union\;
\texttt{AbsentP}\\
&\texttt{SynthRepairNode}(slimit,flip) = \\
& \quad\quad
(  \texttt{Consistancy}\land \texttt{Property} \land
\texttt{FixedForNodeRepair} \land \texttt{FlipN}(slimit,flip) )
\end{align*}
A satisfying model of $\texttt{SynthRepairNode}(slimit,flip)$ will assign some
$flip$ bits to true.
We will learn from the assignments the needed modifications in the VTS.
